Untitled

### 2021-01-13 ms/manuscript.Rmd
Add combined phylogeny + trait data figure

```{r load-data}
tar_load(refs)
tar_load(refs_other)
tar_load(climate)
tar_load(filmy_species)
tar_load(moorea_sites)
tar_load(phylosig)
tar_load(range_types)
tar_load(combined_species_means)
tar_load(t_test_results)
tar_load(env_range_dt_model_summary)
tar_load(recovery_species_means)
tar_load(filmy_habit)
```

@@

```{r plot-setup}
original_theme <- theme_set(theme_bw(base_size = 10))
# JPR requirements:
# Figures should be 39 mm, 84 mm, 129 mm, or 174 mm wide and not higher than 234 mm
# In inches, widths: 1.53, 3.31, 5.08, 6.85; height: 9.21
```

@@

>>>>

```{r load-data}
tar_load(refs)
tar_load(refs_other)
tar_load(climate)
tar_load(filmy_species)
tar_load(moorea_sites)
tar_load(phylosig)
tar_load(range_types)
tar_load(combined_species_means)
tar_load(t_test_results)
tar_load(env_range_dt_model_summary)
tar_load(recovery_species_means)
tar_load(filmy_habit)
tar_load(filmy_phy)
```

@@

```{r plot-setup}
# JPR requirements:
# Figures should be 39 mm, 84 mm, 129 mm, or 174 mm wide and not higher than 234 mm
# In inches, widths: 1.53, 3.31, 5.08, 6.85; height: 9.21

# Set overall theme, saving default theme
default_theme <- theme_set(theme_bw(base_size = 10))

# Define function for formatting text in legends
pretty_text <- function (x) {
  x %>%
  str_replace_all("_", " ") %>%
    str_to_sentence()
}
```

@@

```{r combined-plot, fig.width = 6.85, fig.height = 5, fig.cap = ""}
# Copy phylogeny and species means data so they
# can be manipulated for this plot
phy <- filmy_phy
traits <- combined_species_means

# Set colors for growth habit, generation
habit_colors <- c(
  "Terrestrial" = cbPalette[["red"]], 
  "Saxicolous" = cbPalette[["gold"]], 
  "Low_Epiphyte" = cbPalette[["green"]],
  "High_Epiphyte" = cbPalette[["blue"]])

generation_colors <- c(
  "gametophyte" = "grey70",
  "sporophyte" = "grey30"
)

# Subset tree to only species with trait data
phy <- drop.tip(phy, setdiff(phy$tip.label, traits$species))

# Sort species by position in phylogeny
traits <-
  traits %>%
  filter(species %in% phy$tip.label) %>%
  mutate(species = factor(species, levels = jntools::get_tips_in_ape_plot_order(phy)))

filmy_habit <-
  filmy_habit %>%
  filter(species %in% phy$tip.label)

# Part a (left): tree
a <- ggtree(phy) %<+% filmy_habit +
  geom_tippoint(aes(color = habit), position = position_nudge(x = 7, y = 0), size = 4) +
  scale_color_manual(values = habit_colors, labels = pretty_text) +
  labs(color = "Growth habit")

# Part b (middle): desiccation tolerance
b <- 
ggplot(traits, aes(y = species, x = recovery_mean, fill = generation)) +
  geom_col(position = position_dodge(0.5, preserve = "single"), width = 0.5) +
  geom_errorbarh(
    aes(xmax = recovery_mean + recovery_sd, xmin = recovery_mean),
    position = position_dodge(0.5, preserve = "single"),
    height = 0,
    color = "grey20") +
  scale_x_continuous(
    labels = percent, 
    limits = c(0,1.2), 
    expand = expansion(mult = c(0,0.025)), 
    breaks=c(0,.25,.5,.75,1.0)) +
  scale_fill_manual(values = generation_colors, labels = pretty_text) +
  theme_bw(base_size = 10) +
  labs(x = "Recovery", fill = "Generation") +
  theme(
    panel.grid.minor = element_blank(), 
    panel.grid.major.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom"
  )

# Part c (right): light-levels
c <-
ggplot(traits, aes(y = species, x = etr_mean, fill = generation)) +
  geom_col(position = position_dodge(0.5, preserve = "single"), width = 0.5) +
  geom_errorbarh(
    aes(xmax = etr_mean + etr_sd, xmin = etr_mean),
    position = position_dodge(0.5, preserve = "single"),
    height = 0,
    color = "grey20") +
  theme_bw(base_size = 10) +
  scale_fill_manual(values = generation_colors, labels = pretty_text) +
  scale_y_discrete(
    position = "right",
    # Format species names by converting underscore to space and italicizing
    labels = function(x) str_replace_all(x, "_", " ") %>% paste0("*", ., "*")
    ) +
  scale_x_continuous(expand = expansion(mult = c(0,0.025))) +
  labs(x = "ETR<sub>max</sub>", fill = "Generation") +
  theme(
    panel.grid.minor = element_blank(), 
    panel.grid.major.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y.right = element_markdown(), # NOT axis.text.y
    axis.title.x = element_markdown()
  ) +
  guides(fill = "none")

# Combine plots
a + b + c + plot_layout(nrow = 1, guides = "collect") &
  theme(
    legend.position = "bottom",
    # Adjust invididual margins to remove whitespace between subplots
    plot.margin = margin(t = 0.1, r = 0, b = 0.1, l = 0.04, unit = "in"))

ggsave(here::here("results/ms/fig_combined.pdf"), width = 6.85, height = 5)
```

**`r figure("combined")`**
